Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-01-16 apples_and_oranges.qmd
I think I have fixed the problem with filtering IDs for the CBT, fluox, esc meta regression.

# Here I am creating a new column for df_long_for_metan, to be able to identify which studies featured a condition of interest. 
# for CBT, fluox, esc. I am calling this cfe
cbt_fluox_esc_study_ids <- df_with_distinct_instruments %>%
  filter(active_type %in% c("cbt", "Fluoxetine", "Escitalopram")) %>%
  pull(new_study_id)
df_with_distinct_instruments <- df_with_distinct_instruments %>%
  mutate(key1 = ifelse(new_study_id %in% cbt_fluox_esc_study_ids, 1, NA))

# for wl 
wl_study_ids <- df_with_distinct_instruments %>%
  filter(control_type == "wl") %>%
  pull(new_study_id)
df_with_distinct_instruments <- df_with_distinct_instruments %>%
  mutate(key2 = ifelse(new_study_id %in% wl_study_ids, 2, NA))

# for wl and cau
wl_or_cau_study_ids <- df_with_distinct_instruments %>%
  filter(control_type %in% c("wl", "cau")) %>%
  pull(new_study_id)
df_with_distinct_instruments <- df_with_distinct_instruments %>%
  mutate(key3 = ifelse(new_study_id %in% wl_or_cau_study_ids, 3, NA))

# for cdrs only
cdrs_study_ids <- df_with_distinct_instruments %>%
  filter(instrument_name == "cdrs") %>%
  pull(new_study_id)
df_with_distinct_instruments <- df_with_distinct_instruments %>%
  mutate(key4 = ifelse(new_study_id %in% cdrs_study_ids, 4, NA))

df_with_distinct_instruments <- df_with_distinct_instruments %>%
  mutate(key = paste(key1, key2, key3, key4, sep = "_"))

# Step 2: turn dataframes to long
# A: turn long the rows with active
active_df <- df_with_distinct_instruments %>% 
  dplyr:: select(new_study_id, key, descr_active, psy_or_med, baseline_n_active, cohens_d_active,
                 baseline_mean_active, baseline_sd_active, post_mean_active, post_sd_active) %>% 
  rename(treatment = descr_active) %>% 
  rename_with(~ str_remove(., "_active")) %>% 
  mutate(arm_effect_size = "cohens_d_active") %>% # chose this clunky name because I had used this variable name in previous code and don't want to bread the rest
  group_by(new_study_id) %>% #go through each study id and remove duplicates
  distinct(treatment, .keep_all = TRUE)

control_df <- df_with_distinct_instruments %>% 
  dplyr:: select(new_study_id, key, descr_control, psy_or_med, baseline_n_control, cohens_d_control,
                 baseline_mean_control, baseline_sd_control,post_mean_control, post_sd_control) %>% 
  rename(treatment = descr_control) %>% 
  rename_with(~ str_remove(., "_control")) %>% 
  mutate(arm_effect_size = "cohens_d_control") %>% #chose this clunky name because I had used this variable name in previous code and don't want to bread the rest
  group_by(new_study_id) %>% #go through each study id and remove duplicates
  distinct(treatment, .keep_all = TRUE)

@@

# save this as the master dataframe  --------------------------------------
# use this datafram to perform all operations below in quarto
# ask Charlotte to check steps above (lines 986 to 1121)
write.csv(df_long_for_metan, "df_long_for_metan.csv", row.names = F)

@@

# use those ids to subset all dataframes in the list
list_cbt_fluox_esc_study <- list()

  list_cbt_fluox_esc_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
                                                          %in% cbt_fluox_esc_study_ids,]

# count the number of studies
study_count_cbt_fluox_esc_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% cbt_fluox_esc_study_ids,])
# CHARLOTTE please check. CB - come back to this, possible problem.

>>>>

# Step 2: turn dataframes to long
# A: turn long the rows with active
active_df <- df_with_distinct_instruments %>% 
  dplyr:: select(new_study_id, active_type, descr_active, psy_or_med, baseline_n_active, cohens_d_active,
                 baseline_mean_active, baseline_sd_active, post_mean_active, post_sd_active) %>% 
  rename(treatment = descr_active) %>% 
  rename(type = active_type) %>% 
  rename_with(~ str_remove(., "_active")) %>% 
  mutate(arm_effect_size = "cohens_d_active") %>% # chose this clunky name because I had used this variable name in previous code and don't want to bread the rest
  group_by(new_study_id) %>% #go through each study id and remove duplicates
  distinct(treatment, .keep_all = TRUE)

control_df <- df_with_distinct_instruments %>% 
  dplyr:: select(new_study_id, control_type, descr_control, psy_or_med, baseline_n_control, cohens_d_control,
                 baseline_mean_control, baseline_sd_control,post_mean_control, post_sd_control) %>% 
  rename(treatment = descr_control) %>% 
  rename(type = control_type) %>% 
  rename_with(~ str_remove(., "_control")) %>% 
  mutate(arm_effect_size = "cohens_d_control") %>% #chose this clunky name because I had used this variable name in previous code and don't want to bread the rest
  group_by(new_study_id) %>% #go through each study id and remove duplicates
  distinct(treatment, .keep_all = TRUE)

@@

# save this as the master dataframe  --------------------------------------
# use this dataframe to perform all operations below in quarto
# ask Charlotte to check steps above (lines 986 to 1121)
write.csv(df_long_for_metan, "df_long_for_metan.csv", row.names = F)

#this will be important later in checking for multi arm psy studies 
check_active_dups <- df_long_for_metan %>%
  filter(new_study_id %in% cbt_fluox_esc_study_ids) %>% 
  filter (psy_or_med == 1) %>% 
  group_by(new_study_id) %>%
  filter(n() >= 3)
write.csv(check_active_dups, "check_active_dups.csv")

@@

# Use those ids to subset all dataframes in the list
# By searching for IDs we have mistakenly included multiple active arms. E.g. for Atkinson which has dulox and fluox. 
# So we need to further subset the simulated dfs. For the active arms, I am filtering out conditions that do not meet our criterion. 
# This leaves all the control conditions from trials where the active is cbt, fluox or esc. 
# We may have multiple controls per study id for this reason, though this isn't a problem 
# conceptually.

list_cbt_fluox_esc_study <- lapply(list_df_simulated, function(df) {
  df %>%
    filter(new_study_id %in% cbt_fluox_esc_study_ids) %>%
    filter(!(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt"))))
})

# count the number of studies
cbt_fluox_esc_study <- df_long_for_metan %>%
  filter(new_study_id %in% cbt_fluox_esc_study_ids,
         !(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt")))) 
study_count_cbt_fluox_esc_study <- count_studies(cbt_fluox_esc_study)
